---
title: "Full Pipeline"
output: pdf_document
author: "Jamie Prentice"
date: "2021-01-26"
---

## Overview

Create simulated epidemic data and send to SIRE 2.0. Eventually intend to
replace simulated data with Turbot data.

R functions based on Richard Bailey's originals. [SIRE
2.0](https://github.com/theITEAM/SIRE2.0/) modified from Chris Pooley's
original.


```{r include = FALSE}
# Load libraries and source files
library(data.table) # used for all data table manipulations
library(xml2)       # used to generate XML file
library(corpcor)    # efficient estimation of Cov and (partial) Corr
library(MASS)
library(MCMCglmm)
```

## Load source files

```{r}
setwd("~/Dropbox/Roslin/pipeline")

# source("parameters.R")
source("pedigree_grm-old.R")
source("pedigree_grm.R")
source("make_traits.R")
source("episim3.R")
source("episim3-new.R")
source("group_assignment.R")
source("discrete_time.R")
source("data_table_to_tsv_string.R")
```

## Parameters

Population numbers
```{r}
# No. of sires, dams per sire, and offspring per pair, and groups
nsire <- 10
dpsire <- 5
oppair <- 2
ngroups <- 2

# Derived population numbers
ndam = nsire * dpsire
nparent = nsire + nsire * dpsire
nprogeny = nsire * dpsire * oppair
nind = nprogeny

# TODO: I think it should be this, but we'll keep it as is for the moment
nind = nparent + nprogeny

# TODO: what if this isn't an integer?
group_size = nprogeny / ngroups
```

Traits
```{r}
# Names
traitnames <- c("susceptibility", "infectivity", "recoverability")
# No. of traits to simulate.
ntraits <- length(traitnames)
# Trait means
tmeans <- rep(0, ntraits)
# Trait additive genetic variance
tVA <- c(0.5, 0.1, 0.1)
# Trait non-additive (environmental) variance
# with no association to the pedigree
tVE <- c(0.3, 0.3, 0.3)
# Trait non-additive correlation matrix
trhoE <- diag(ntraits)
# Trait additive genetic correlation matrix.
# In this case correlations are zero.
trhoG <- diag(ntraits)
```

Infection and recoverability, targeting `R0 = 2.5`?
```{r}
PairwiseBeta <- 0.1
RRgamma <- 0.2
```

MCMC settings
```{r}
nsample <- 5000
burnin <- 500
```

Additional options
```{r}
trim_parents <- FALSE
DEBUG <- FALSE
```

This will be a list for passing to functions
```{r}
pars <- list(nsire = nsire, ndam = ndam, nprogeny = nprogeny, nind = nind, ngroups = ngroups,
             traitnames = traitnames, ntraits = ntraits, tmeans = tmeans,
             tVA = tVA, tVE = tVE, trhoE = trhoE, trhoG = trhoG,
             PairwiseBeta = PairwiseBeta, RRgamma = RRgamma,
             nsample = nsample, burnin = burnin,
             trim_parents = trim_parents, DEBUG = DEBUG)

# Quickly summarise what we've got
cat(with(pars, paste0(
    "Generating data with:\n",
    nsire, " sires, ",
    ndam, " dams, ",
    nprogeny, " progeny, (",
    nind, " individuals), ",
    ngroups, " groups\n",
    "R0 = ", PairwiseBeta / RRgamma, "?\n"
)))
```
